Democracy, Public Support, and Measurement Uncertainty

### 2021-05-13 paper/dcpo_demsupport.Rmd
codes for combining theta and control variables

>>>>

cntrl_ajps_uncertainty <- readRDS("data/cntrl_ajps_uncertainty.rds")

dcpo_analysis <- left_join(df_dcpo,cntrl_ajps_uncertainty, by=c("country","year","iter"="iter_se") )
saveRDS(dcpo_analysis, "data/dcpo_analysis_ajps.rds")

cls_ajps_uncertainty <- readRDS("data/cls_ajps_uncertainty.rds")

cls_analysis <- left_join(cls_theta_uncertainty,cls_ajps_uncertainty, by=c("country","year"="Year","iter"="iter_se") )
saveRDS(cls_analysis, "data/cls_analysis_ajps.rds")
